---
title: "ANLY 503 Portfolio"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
```

Introduction
=====================================  


<pre></pre>
<pre></pre>

##### This website contains some of the homework and the final project of ANLY 503. For more information, please check the following GitHub repo for the full version of all homework assignments.
##### https://github.com/evelynnmeow/ANLY503Portfolio

</pre>
</pre>
Data Munging Part 1
=====================================  
Column {data-width=650}
-----------------------------------------------------------------------
<pre></pre>
<pre></pre>
<pre></pre>
<pre></pre>
### Before Munging

```{r}
 #read in the data
loan = read.csv("data1/data/loans.csv")
head(loan)
```

-----------------------------------------------------------------------

### After Munging
```{r}
# collect information of loands
df1 = loan %>% pivot_longer(cols = X24_A:X60_A, names_to = 'demo', values_to = 'status')

# extract the loan type and duration
f2 = df1 %>% 
  extract(demo, c('duration', 'type'), regex = 'X([0-9][0-9])[_]([A-Z])')

# Since one account can only have one load, drop any loan that status is not X
# also drop the status col since it is irrelevant
loan_final = f2 %>% filter(status== 'X') %>% select(-status)
head(loan_final)




```
</pre>
</pre>
</pre>
</pre>
Data Munging Part 2
=====================================  
Column {data-width=650}
-----------------------------------------------------------------------
<pre></pre>
<pre></pre>
<pre></pre>
<pre></pre>
### Before Munging

```{r}
# read in the data
df = read.csv('data1/data/districts.csv')
head(df)
```


### After Munging
```{r}
# extract info of municipality info column
df1 = df %>% 
  extract(municipality_info, 
          c('pop_lessn_500', 'pop_500_1999', 'pop_2000_9999', 'pop_greater_10000'), 
          regex = '\\[([0-9]+)[,]+([0-9]+)[,]+([0-9]+)[,]+([0-9]+)\\]')


# extract the unemployment rate from 95 and 96
df2 = df1 %>% 
  extract(unemployment_rate, c('unemployment_rate_95', 'unemployment_rate_96'),
          regex = '\\[([0-9]+.[0-9]+)[,]+([0-9].[0-9]+)\\]')


# extract commited crimes from 95 and 96
df3 = df2 %>% 
  extract(commited_crimes, c('commited_crimes_95', 'commited_crimes_96'), 
          regex = '\\[([0-9]+)[,]+([0-9]+)\\]')

head(df3)
```

</pre>
</pre>
</pre>
</pre>
ScatterPlots
=====================================  
<pre></pre>
<pre></pre>
<pre></pre>
<pre></pre>
Column {data-width=800}
-----------------------------------------------------------------------

```{r}
# read in the data
trans = read_csv("HW5/data/transactions.csv")
accounts = read_csv("HW5/data/accounts_analytical.csv")
df = accounts %>% filter(!is.na(loan_amount))
p1 = ggplot(data=df, aes(x=account_id, y=loan_amount)) +
  geom_point(size = 0.05) + labs(title="Scatterplot of loan amount", 
         x="Account ID", y = "Loan Amount")

p1
```

```{r}
df1 = accounts %>% mutate(credit_card = ifelse(is.na(credit_cards), "No credit card", "Has credit cards"))
p1 = ggplot(data = df1, 
       mapping = aes(x = account_id, 
                     y = debit_credit_card_other_txn_ct, 
                     color = credit_card)) +
  geom_point(size = 0.1, alpha =0.5) + labs(title="Credit card transaction count", 
         x="Accound ID", y = "Credit card transaction count")

p1
```

Column {data-width=800}
-----------------------------------------------------------------------

```{r}
p2 = ggplot(data = df1, 
       mapping = aes(x = account_id, 
                     y = debit_credit_card_other_txn_tot, 
                     color = credit_card)) +
  geom_point(size = 0.1, alpha =0.5) + labs(title="Credit card transaction total", 
         x="Accound ID", y = "Credit card transaction total")

p2

```

```{r}
p3 = ggplot(data = df1, 
       mapping = aes(x = account_id, 
                     y = debit_credit_card_other_avg_txn, 
                     color = credit_card)) +
  geom_point(size = 0.1, alpha =0.5) + labs(title="Credit card transaction average", 
         x="Accound ID", y = "Credit card transaction average")

p3

```

</pre>
</pre>
</pre>
</pre>

Histograms
=====================================  
<pre></pre>
<pre></pre>
<pre></pre>
<pre></pre>
Column {data-width=800}
-----------------------------------------------------------------------
```{r}
df = accounts %>% filter(!is.na(loan_amount))
p2 = ggplot(df, aes(x=loan_amount)) + geom_histogram(color="black", fill="lightblue") + labs(title="Histogram of Loan Amount", 
         x="Loan Amount", y = "Count")
p2
```
```{r}
p6 = ggplot(df, aes(x=loan_payment)) + geom_histogram(color="black", fill="lightblue") + labs(title="Histogram of Loan Payment", 
         x="Loan Payment", y = "Count")
p6
```

Column {data-width=800}
-----------------------------------------------------------------------

```{r}
p7 = ggplot(df, aes(x=loan_date)) + geom_histogram(color="black", fill="lightblue") + labs(title="Histogram of Loan Date", 
         x="Loan Date", y = "Count")
p7

```

```{r}
df1 = df %>% mutate(days = loan_date - acct_creation_date)
default = df1 %>% filter(loan_default == T)
# dirstribution of days 
p2 = ggplot(df1, aes(x=days)) + geom_histogram(color="black", fill="lightblue") + labs(title="Histogram of Days", 
         x="Days", y = "Count") + facet_grid(cols = vars(loan_default))
p2

```


```{r, echo =FALSE}
# read in the dataset
sephora = read.csv("final/data/products.csv", header = T) 
chemical = read.csv("final/data/cscpopendata.csv", header = T)
ingredients = read.csv("final/data/ingredients.csv", header = T)

```

```{r, echo = FALSE}
# select useful features 
short = ingredients %>% select(code, product_name, main_category_en, quantity, 
                               brands, manufacturing_places, countries_en, ingredients_text, 
                               additives_n, additives_en, 
                               states_en)
# filter out NAs
ingredient = short %>% filter(product_name != "") %>% filter(main_category_en != "") %>% filter(ingredients_text != "") 

```

```{r, echo = FALSE}
# create my own color theme
library(ggplot2)

theme_set(theme_minimal())

custom_colors <- c(
  `pink`      = "#ffd4df",
  `red`        = "#ff4101",
  `purple`     = "#8A2BE2",
  `green`      = "#dfffd4",
  `blue`       = "#d4f5ff",
  `yellow`     = "#fff4d4",
  `light grey` = "#cccccc",
  `dark grey`  = "#8c8c8c")

custom_cols <- function(...) {
  cols <- c(...)

  if (is.null(cols))
    return (custom_colors)

  custom_colors[cols]
}

custom_palettes <- list(
  `main`  = custom_cols("pink", "blue", "green"),

  `cool`  = custom_cols("blue", "green"),

  `warm`   = custom_cols("pink", "red"),

  `mixed` = custom_cols("blue", "green", "purple", "light grey", "red"),

  `grey`  = custom_cols("light grey", "dark grey")
)

custom_pal <- function(palette = "main", reverse = FALSE, ...) {
  pal <- custom_palettes[[palette]]

  if (reverse) pal <- rev(pal)

  colorRampPalette(pal, ...)
}

scale_color_custom <- function(palette = "main", discrete = TRUE, reverse = FALSE, ...) {
  pal <- custom_pal(palette = palette, reverse = reverse)

  if (discrete) {
    discrete_scale("colour", paste0("custom_", palette), palette = pal, ...)
  } else {
    scale_color_gradientn(colours = pal(256), ...)
  }
}

scale_fill_custom <- function(palette = "main", discrete = TRUE, reverse = FALSE, ...) {
  pal <- custom_pal(palette = palette, reverse = reverse)

  if (discrete) {
    discrete_scale("fill", paste0("custom_", palette), palette = pal, ...)
  } else {
    scale_fill_gradientn(colours = pal(256), ...)
  }
}

```

```{r, echo = FALSE}
# get the number of cases reported in primary category
primary_cat = chemical %>% group_by(PrimaryCategory) %>% count
# get the number of cases reported in makeup
makeup = chemical %>% filter(PrimaryCategoryId == 44)
sub_cat = makeup %>% group_by(SubCategory) %>% count
# get the number of cases reported in lip color
lips = makeup %>% filter(SubCategoryId == 53)
lips_cat = lips %>% group_by(ChemicalName) %>% count %>% arrange(desc(n)) %>% head(4) 
```

```{r, echo = FALSE}
# sentiment analysis
# import library
library(stringr)
library(tidytext)
#head(sephora)
# lip products
lip = sephora %>% filter(product_type == "\nLipstick\n" |  product_type == "\nLipgloss\n") %>% select(ID, description)

# sentiments dataset
sents = get_sentiments("afinn")

# unnest and join
t1 = lip %>% mutate(des = as.character(description)) %>% unnest_tokens(word, des)
des_sent = left_join(t1, sents, by = "word")

df1 = des_sent %>% filter(!is.na(value)) %>% group_by(value) %>% count
```


```{r, echo = FALSE}
# titanium dioxide in all categories
tio2 = chemical %>% filter(ChemicalName == "Titanium dioxide")
# head(tio2)
ti_cat = tio2 %>% group_by(PrimaryCategory) %>% count
ti_date = tio2 %>% group_by(InitialDateReported) %>% count

# manipulate the data
# change the data from char to datetime object
library(lubridate) 
ti_date1 = ti_date %>% mutate(date = as.Date(InitialDateReported, "%m/%d/%Y"))

```

```{r, echo = FALSE}
# get all retinol products
retinol = chemical %>% filter(ChemicalName == "Retinol")
# get the date
re_date = retinol %>% group_by(InitialDateReported) %>% count
re_date1 = re_date %>% mutate(date = as.Date(InitialDateReported, "%m/%d/%Y"))


```

```{r, echo = FALSE}
# read in the world map
world_map <- map_data("world")
# read in the active ingredient data
additive = read.csv("final/data/additive.csv", header = T)

```
</pre>
</pre>
</pre>
</pre>
Network Graph and Geographical Graph
=====================================  
<pre></pre>
<pre></pre>
<pre></pre>
<pre></pre>
### Network Graph
```{r, echo = FALSE}
library(GGally)
library(network)
```
````{r}
# set seed
set.seed(919)
# get a random sample of 50
chem_work =chemical %>% select(ChemicalId, PrimaryCategoryId) %>% drop_na() %>% sample_n(50)
# change the type to char
chem_work$ChemicalId <- as.character(chem_work$ChemicalId)
chem_work$fPrimaryCategoryId <- as.character(chem_work$PrimaryCategoryId)
```

```{r}
# build the network
nw <- network(chem_work, directed = TRUE, matrix.type = "edgelist")

```

```{r}
# draw the plot
ggnet2(net = nw, 
       color = "pink",
       label = TRUE, 
       label.size = 3,
       arrow.size = 0.3, 
       arrow.gap = .03)

```

### Geographical Graph
```{r}
# lop the world map
world <- map_data("world")
# plot the world map
p8 = ggplot() +
  geom_map(
    data = world, map = world,
    aes(long, lat, map_id = region),
    color = "black", fill = "lightgray", size = 0.1
  )  + 
  geom_point(
    data = additive,
    aes(longitude, latitude, color = "pink", size = avg_active_ingredient),
    alpha = 0.7
  ) + 
  labs(title="Average Active Ingredients of Products Sold in Each Country", x = "Longitude", y = "Latitude")
p8

```

</pre>
</pre>
</pre>
</pre>

Final Project Website
=====================================  

<pre></pre>
<pre></pre>





For the final project, please nevigate to:

https://evelynnmeow.github.io/CosmeticIngredientsAnalysis/

</pre>
</pre>

